  \vspace{5 cm}



     
   \begin{center}

 \textbf{Acknowledge} 
\end{center}

It has been a great time doing my PhD at the University of Exeter. I have learned
more than I could ever have anticipated, and grown as a researcher. Here I would like to
acknowledge those without whom this work would not have been possible.

First of all, I would like to thank my father, Prof Ziad Abu hammad, who continues to learn, grow and develop and who has been a
source of encouragement and inspiration to me throughout my life. And to my mother to my mother, Fatima Alsied, known only briefly but loved and missed, who

To my dear wife, Rawaah Alzyod who remains your practical and emotional support, to the competing demands of  work, study and
personal development.

My sone Abdullah

My daughter  Lujain

My littel sone Khaled

To my baby on 

I am forever grateful to my supervisors, Richard Everson and Jonathan Fieldsend, for
this once in a lifetime opportunity. Their knowledge, encouragement, enthusiasm, and
expert supervision were pivotal in the completion of this thesis. I truly cherish all of our
exhilarating discussions throughout my PhD, and I thank them for all their guidance,
patience and time. It has been an honour and a privilege to work with them.

I would like to take this opportunity to thank Khaled Aljaber, Ziad Alzyod,
Khaled Almasri, Ashraf Alsied, Mohammed Almasri, Mohammed Alhorani, Rami ..., Ayah
Karegyesa, Prashanth Srinivas, Jonathan Comley, David Walker, Jacqueline Christmas,
Philip Sansom, Qiong Cao, Imran Sumel, Mainul Islam, Shafkat Chowdhury, Shabab
Choudhury, Jonathan Wilkinson, Tanbirul Hasan, Vaibhav Shah, Raya Seerden, Jonathan
Tsoi and Matthew Bain for their friendship and support.
